Battling Climate Change: Implications on the Canadian Climate Policies in Recent Years

### 2022-04-27 outputs/paper/paper.Rmd
fixed abstract, intro, and citations

---
title: "Battling Climate Change: Implications on the Canadian Climate Policies in Recent Years"
author: 
  - Owen Huang
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In this paper, we have fitted a model to predict the anuual national greenhouse gas emission in Canada, and evaluated against the target of 30% reduction in emissions below the 2005 levels by 2030. With the current data presented, we have high believes that Canada will successfully reach its goal by the year of 2030. This is an important implication as it indicates that it is highly likely that Canada will be able to fulfill its goal as stated in the Paris Agreement. Fulfilling the Paris Agreement is the first step toward mitigating the devastating effects of climate change and providing the future generation with a safe world to live in, not a corrupted one."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(ggpubr)
library(ggrepel)
library(haven)
library("readxl")
library(readr)
library(lme4)
```

@@

After we obtained the result, we conclude that with the evidence we are presented with, we have strong evidence supporting the hypothesis that by the year 2030, the greenhouse gas emission level will be below that of 2005. This is an important implication as it indicates that it is highly likely that Canada will be able to fulfill its goal as stated in the Paris Agreement. Fulfilling the Paris Agreement is the first step toward mitigating the devastating effects of climate change and providing the future generation with a safe world to live in, not a corrupted one.

@@

Throguhout the analysis of this report, we used $R$ (@1), the $tidyverse$ (@2) package, the $kableExtra$ (@3) package, the $usmap$ (@4) package, the $ggplot2$ (@5) package,the $ggpubr$ (@6) package, and the $readxl$ (@7) package for the data analyzing process and graph plotting. All data and graphs are inspired by Melissa S. Kearney, Phillip B. Levine, and Luke Pardue.

@@

```{r, echo=FALSE, }
canada_data %>% summarise(Variable = c("Year", "Country", "GHG Emissions"),
                          Descriptions = c("Years from 1959 to 2020", 
                                           "Countries containing Australia, Brazil, Canada, USA, China, etc.(total of 12 countries)", 
                                           "the greenhouse gas emissions in million tonnes per year"))%>%
  kable(caption = "GHG Emissions, by country")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```

@@

| Variable | Description                          |
|----------|--------------------------------------|
| Year | 3 specified years: 1990, 2005, 2020                 |
| Province pr Territory     | All the Canadian provinces and territories (ON, BC, etc.)              |
| GHG Emission        | the greenhouse gas emissions in megatons of CO$_2$ equivalent    |

@@

| Variable | Description                          |
|----------|--------------------------------------|
| Year | 3 specified years: 1990, 2005, 2020                 |
| Total     | The total GHG emissions in the specified year, in Mt CO$_2$ eq             |
| Sector       | Economic sectors (oil and gas, transports, buildings, electricity, heavy industry, agriculture, waste and others)   |
| GHG Emission        | the greenhouse gas emissions in Mt CO$_2$ eq     |

Canada's GDP per capita (@10) and population (@11) is obtained from the World Bank national accounts data, and OECD National Accounts data files. (CITATION)

Data on Canada's GDP by expenditure is obtained from Statistics Canada. (CITATION)

@@

```{r, echo=FALSE, fig.height=4,fig.width=7, fig.cap="Canada's GHG emissions, GDP, and population"}
country <- Country_Emissions %>%
  filter(Year>=1990) %>%
  ggplot(aes(x = Year, y = `GHG Emission`, group = country, color=country)) + 
  geom_line()+
  labs(title = "GHG Emission (Mt), by country", y='GHG Emission (Mt)',x='Year')+
  theme_minimal()

@@

ghg_output <- canada_data %>%
  filter(Year >= 1990) %>%
  ggplot(aes(x=Year, y=`Total greenhouse gas emissions (megatonnes of carbon dioxide equivalent)`)) + 
  labs(title = "C: GHG emissions (Megatons)", x="Year", y="GHG emissions (Mt)")+
  geom_point() +
  geom_line()+
  theme_minimal()

@@

```{r, echo=FALSE, fig.height=3,fig.width=7, fig.cap="Canada's GHG emissions, GDP, and population"}
# canada's ghg emission by different sectors
sector_ghg_emissions %>% 
  filter(!is.na(`Megatonnes of carbon dioxide equivalent`)) %>% 
  ggplot() + 
  geom_bar(aes(x= Year, y = Total, fill = sector), stat="identity") + 
  labs(title = "Canada's GHG emission (Mt), by different sectors", y='GHG Emission (Mt)',x='Year') +
  theme_classic()
```

@@

```{r, echo=FALSE, fig.height=3,fig.width=7, warning=FALSE, fig.cap="Canada's GHG emissions, GDP, and population"}
prov_ghg_emissions %>% 
  ggplot(aes(x=`Province or territory`, y=`GHG Emission`, fill=Year)) +
  geom_bar(stat='identity', position='dodge') +
  labs(title = "Canada's GHG emission (Mt), by provinces", y='GHG Emission (Mt)',x='Year') +
  theme_classic()

@@

```{r , echo=FALSE, fig.height=3,fig.width=5, fig.cap="Canada's GHG emissions, GDP, and population"}
r <- resid(final_model)

@@

```{r, echo=FALSE, fig.height=4,fig.width=5, fig.cap="Canada's GHG emissions, GDP, and population"}
par(mfrow=c(2,3))
plot(r ~ fitted(final_model), main="Fitted vs Residual", xlab="Fitted", ylab="res.")
plot(r ~ canada_data$`Gross fixed capital formation`, main="GFCF vs Residua", xlab="GFCF", ylab="res")
plot(r ~ canada_data$Year, main="Year vs Residual", xlab="Year", ylab="res")
plot(r ~ canada_data$`Business gross fixed capital formation`, main="Busniess GFCF vs Residual", xlab="Business GFCF", ylab="res")
plot(r ~ canada_data$`Machinery and equipment`, main="M & E vs Residual", xlab="Machinery and Equipment", ylab="res")
plot(r ~ canada_data$`Exports to other countries`, main="Exports vs Residual", xlab="Export", ylab="res")

>>>>

---
title: "Battling Climate Change: Implications on the Canadian Climate Policies in Recent Years"
author: 
  - Owen Huang
thanks: "Code and data are available at: https://github.com/Ovven999/Climate_Change "
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In this paper, we have fitted a multiple linear regression model to predict the anuual national greenhouse gas (GHG) emission in Canada, and determined that investments in business, machinery equipment, and exports are the economic factors that are contributing the most to Canada's annual GHG emissions. With the current data presented, we are not able to foretell the future trend of Canada's GHG emissions as we cannot quantify how the economy is going to bahave after the pandemic has ended. However, there remains hope as the Government of Canada are actively trying to surpressing the production of GHG, and the innovation of a renewable and green source and energy is imminent. Fulfilling the Paris Agreement (reduce GHG emission levels in 2030 to 30% below the 2005 levels) is the first step toward mitigating the devastating effects of climate change and providing the future generation with a safe world to live in, not a corrupted one."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(ggpubr)
library(ggrepel)
library("readxl")
library(readr)
library(lme4)
```

@@

After we obtained the result, we conclude that with the evidence we are presented with, investments in business, machinery and equipment, and exports are the primary economic factors that are contributing the most to Canada's annual GHG emissions. This can give insights to policy makers to weight the tradeoffs between stimulating investments and limiting GHG emissions. Since the pandemic have stiked the globe in 2020, the most recent data of Canada's GDP and GHG emission levels in 2021 and 2022 has not been revealed, thus we cannot make meaningful predictions on the future trend of the economy and GHG emissions. However, we suggest to keep implementing the current climate change policies such as carbon pricing, promoting zero-emission vehicles, and energy efficiency retrofits for buildings to limit the growth of GHG emission levels, and shift time and resources to research and development branches for innovations in renewable, replenishable, and green energy sources. This would be a more sustainable solution for the long run.

@@

Throguhout the analysis of this report, we used $R$ (@1), the $tidyverse$ (@2) package, the $kableExtra$ (@3) package, the $dplyr$ (@4) package, the $ggplot2$ (@5) package,the $ggpubr$ (@6) package, the $knitr$ (@13) package, the $ggrepel$ (@14) package, the $readr$ package, the $readxl$ (@7) package, and the $lme4$ package for the data analyzing process and graph plotting.

@@

```{r, echo=FALSE, }
canada_data %>% summarise(Variable = c("Year", "Country", "GHG Emissions"),
                          Descriptions = c("Years from 1959 to 2020", 
                                           "Countries containing Australia, Brazil, Canada, USA, China, etc.(total of 12 countries)", 
                                           "the greenhouse gas emissions in million tonnes per year"))%>%
  kable(caption = "GHG Emissions, by country",
        linesep = "")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```

@@

```{r, echo=FALSE, }
canada_data %>% summarise(Variable = c("Year", "Province or Territory", "GHG Emissions"),
                          Descriptions = c("3 specified years: 1990, 2005, 2020", 
                                           "All the Canadian provinces and territories (ON, BC, etc.)", 
                                           "the greenhouse gas emissions in megatons of CO2 equivalent"))%>%
  kable(caption = "Canada's GHG Emissions, by Province or Territory",
        linesep = "")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```

@@

```{r, echo=FALSE, }
canada_data %>% summarise(Variable = c("Year", "Total", "Sector", "GHG Emission"),
                          Descriptions = c("Years from 1990 to 2020", 
                                           "The total GHG emissions in the specified year, in Mt CO2 eq",
                                           "oil and gas, transports, buildings, electricity, heavy industry, agriculture, waste and others",
                                           "the greenhouse gas emissions in megatons of CO2 equivalent, for the sector"))%>%
  kable(caption = "Canada's GHG Emissions, by Province or Territory",
        linesep = "")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```

Canada's GDP per capita (@10) and population (@11) is obtained from the World Bank national accounts data, and OECD National Accounts data files. Data on Canada's GDP by expenditure is obtained from Statistics Canada (@12). We have organized the data sets into one as follows. Notice that GDP expenditure have many more sub-categories, here we are only listing a few imporantant ones.

```{r, echo=FALSE, }
canada_data %>% summarise(Variable = c("Year", "GDP per capita", "GDP", "Population", "GHG emissions", "Final Consumption Expenditure", "Gross Fixed Capital Formation", "Exports", "Imports"),
                          Descriptions = c("Years from 1990 to 2020", 
                                           "Country's GDP divided by its population",
                                           "THe Gross Domestic Product in Canada",
                                           "The Canada's total population",
                                           "The total GHG emissions in the specified year, in Mt CO2 eq",
                                           "Include consumption by households, institutions, and government",
                                           "Country's total investment",
                                           "Exports to other countries",
                                           "Imports from other countries"))%>%
  kable(caption = "Canada's GDP, population, and GHG emissions, by year",
        linesep = "")%>%
  kable_styling(latex_options = "HOLD_position")%>%
  add_header_above()
```

@@

```{r, echo=FALSE, fig.height=4,fig.width=7, fig.cap="GHG Emission (Mt), by country"}
country <- Country_Emissions %>%
  filter(Year>=1990) %>%
  ggplot(aes(x = Year, y = `GHG Emission`, group = country, color=country)) + 
  geom_line()+
  labs(title = "GHG Emission (Mt), by country", y='GHG Emission (Mt)',x='Year')+
  theme_minimal()

@@

ghg_output <- canada_data %>%
  filter(Year >= 1990) %>%
  ggplot(aes(x=Year, y=`Total greenhouse gas emissions (megatonnes of carbon dioxide equivalent)`)) + 
  labs(title = "C: GHG emissions (Megatons)", x="Year", y="Mt CO2 eq")+
  geom_point() +
  geom_line()+
  theme_minimal()

@@

```{r, echo=FALSE, fig.height=3,fig.width=7, fig.cap="Canada's GHG emission (Mt CO2 eq), by different sectors"}
# canada's ghg emission by different sectors
sector_ghg_emissions %>% 
  filter(!is.na(`Megatonnes of carbon dioxide equivalent`)) %>% 
  ggplot() + 
  geom_bar(aes(x= Year, y = Total, fill = sector), stat="identity") + 
  labs(title = "Canada's GHG emission (Mt), by different sectors", y='GHG Emission (Mt)',x='Year') +
  theme_classic()
```

@@

```{r, echo=FALSE, fig.height=3,fig.width=7, warning=FALSE, fig.cap="Canada's GHG emission (Mt CO2 eq), by provinces"}
prov_ghg_emissions %>% 
  ggplot(aes(x=`Province or territory`, y=`GHG Emission`, fill=Year)) +
  geom_bar(stat='identity', position='dodge') +
  labs(title = "Canada's GHG emission (Mt), by provinces", y='GHG Emission (Mt)',x='Year') +
  theme_classic()

@@

```{r , echo=FALSE, fig.height=3,fig.width=5, fig.cap="Checking for multiple linear regression assumptions: Y vs Y_hat and QQ plot"}
r <- resid(final_model)

@@

```{r, echo=FALSE, fig.height=4,fig.width=5, fig.cap="Check for the residual plots of the multiple linear regression model"}
par(mfrow=c(2,3))
plot(r ~ fitted(final_model), main="Fitted vs Residual", xlab="Fitted", ylab="res.")
plot(r ~ canada_data$`Gross fixed capital formation`, main="GFCF vs Residua", xlab="GFCF", ylab="res")
plot(r ~ canada_data$Year, main="Year vs Residual", xlab="Year", ylab="res")
plot(r ~ canada_data$`Business gross fixed capital formation`, main="Busniess GFCF vs Residual", xlab="Business GFCF", ylab="res")
plot(r ~ canada_data$`Machinery and equipment`, main="M & E vs Residual", xlab="Machinery and Equipment", ylab="res")
plot(r ~ canada_data$`Exports to other countries`, main="Exports vs Residual", xlab="Export", ylab="res")
